### 2022-03-03 tables/paper2/table-1-desc.tex
fix paper 1 tables, finish most of writing

\begin{table}[!h]

\caption{\label{tab:table-1-desc}Descriptive Statistics for Dichotomous and Numeric Variables}
\centering
\begin{tabular}[t]{lrr}
\toprule
  & Mean & SD\\
\midrule
\cellcolor{gray!6}{Received info} & \cellcolor{gray!6}{\num{0.66}} & \cellcolor{gray!6}{\num{0.47}}\\
Received info, Doctor & \num{0.47} & \num{0.50}\\
\cellcolor{gray!6}{Received info, Person} & \cellcolor{gray!6}{\num{0.67}} & \cellcolor{gray!6}{\num{0.47}}\\
Received info, News & \num{0.65} & \num{0.48}\\
\cellcolor{gray!6}{Received info, Social Networking Site} & \cellcolor{gray!6}{\num{0.40}} & \cellcolor{gray!6}{\num{0.49}}\\
Received info, Online Forum & \num{0.35} & \num{0.48}\\
\cellcolor{gray!6}{Sought Info} & \cellcolor{gray!6}{\num{0.78}} & \cellcolor{gray!6}{\num{0.41}}\\
Sought Info, Doctor & \num{0.44} & \num{0.50}\\
\cellcolor{gray!6}{Sought Info, Person} & \cellcolor{gray!6}{\num{0.42}} & \cellcolor{gray!6}{\num{0.49}}\\
Sought Info, Social Networking Site & \num{0.18} & \num{0.39}\\
\cellcolor{gray!6}{Sought Info, Online Forum} & \cellcolor{gray!6}{\num{0.27}} & \cellcolor{gray!6}{\num{0.44}}\\
Sought Info, Online Search & \num{0.41} & \num{0.49}\\
\cellcolor{gray!6}{Vaccination Status} & \cellcolor{gray!6}{\num{0.84}} & \cellcolor{gray!6}{\num{0.36}}\\
Vaccination Outlook & \num{0.87} & \num{0.34}\\
\cellcolor{gray!6}{Age} & \cellcolor{gray!6}{\num{37.76}} & \cellcolor{gray!6}{\num{10.75}}\\
Hispanic or Latino/x & \num{0.15} & \num{0.36}\\
\cellcolor{gray!6}{Race, White} & \cellcolor{gray!6}{\num{0.88}} & \cellcolor{gray!6}{\num{0.33}}\\
Race, Black & \num{0.08} & \num{0.27}\\
\cellcolor{gray!6}{Race, Native American} & \cellcolor{gray!6}{\num{0.03}} & \cellcolor{gray!6}{\num{0.16}}\\
Race, Asian or Pacific Islander & \num{0.04} & \num{0.20}\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.74}} & \cellcolor{gray!6}{\num{0.44}}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]

\caption{\label{tab:table-1-desc}Descriptive Statistics for Dichotomous and Numeric Variables}
\centering
\begin{tabular}{lrr}
\toprule
  & Mean & SD\\
\midrule
Received info & \num{0.66} & \num{0.47}\\
Received info, Doctor & \num{0.47} & \num{0.50}\\
Received info, Person & \num{0.67} & \num{0.47}\\
Received info, News & \num{0.65} & \num{0.48}\\
Received info, Social Networking Site & \num{0.40} & \num{0.49}\\
Received info, Online Forum & \num{0.35} & \num{0.48}\\
Sought Info & \num{0.78} & \num{0.41}\\
Sought Info, Doctor & \num{0.44} & \num{0.50}\\
Sought Info, Person & \num{0.42} & \num{0.49}\\
Sought Info, Social Networking Site & \num{0.18} & \num{0.39}\\
Sought Info, Online Forum & \num{0.27} & \num{0.44}\\
Sought Info, Online Search & \num{0.41} & \num{0.49}\\
Vaccination Status & \num{0.84} & \num{0.36}\\
Vaccination Outlook & \num{0.87} & \num{0.34}\\
Age & \num{37.76} & \num{10.75}\\
Hispanic or Latino/x & \num{0.15} & \num{0.36}\\
Race, White & \num{0.88} & \num{0.33}\\
Race, Black & \num{0.08} & \num{0.27}\\
Race, Native American & \num{0.03} & \num{0.16}\\
Race, Asian or Pacific Islander & \num{0.04} & \num{0.20}\\
Associate's Deg or above & \num{0.74} & \num{0.44}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

### 2022-03-03 tables/paper2/table-2-desc.tex
fix paper 1 tables, finish most of writing

\begin{table}[!h]

\caption{\label{tab:table-2-desc}Descriptive Statistics for Categorical Variables}
\centering
\begin{tabular}[t]{llrr}
\toprule
  &    & N & Percent\\
\midrule
\cellcolor{gray!6}{Gender} & \cellcolor{gray!6}{Female} & \cellcolor{gray!6}{418} & \cellcolor{gray!6}{\num{44.09}}\\
 & Male & 524 & \num{55.27}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Other} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{\num{0.63}}\\
Highest Education Level & Graduate or professional degree & 145 & \num{15.30}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Bachelor's degree} & \cellcolor{gray!6}{560} & \cellcolor{gray!6}{\num{59.07}}\\
 & Associate's or Technical degree & 72 & \num{7.59}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Some college} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{\num{10.55}}\\
 & High school graduate & 68 & \num{7.17}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Less than high school} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{\num{0.32}}\\
Plan to be Vaccinated if not & Probably not & 38 & \num{4.01}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Definitely yes} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{\num{1.37}}\\
 & Definitely not & 61 & \num{6.43}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Might or might not} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{\num{2.32}}\\
 & Probably yes & 13 & \num{1.37}\\
\cellcolor{gray!6}{Found Info Sought Useful} & \cellcolor{gray!6}{Very useful} & \cellcolor{gray!6}{345} & \cellcolor{gray!6}{\num{36.39}}\\
 & Moderately useful & 112 & \num{11.81}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Extremely useful} & \cellcolor{gray!6}{264} & \cellcolor{gray!6}{\num{27.85}}\\
 & Slightly useful & 18 & \num{1.90}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Not at all useful} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{\num{0.21}}\\
Census Region & Midwest & 171 & \num{18.04}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Northeast} & \cellcolor{gray!6}{170} & \cellcolor{gray!6}{\num{17.93}}\\
 & South & 365 & \num{38.50}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{West} & \cellcolor{gray!6}{223} & \cellcolor{gray!6}{\num{23.52}}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]

\caption{\label{tab:table-2-desc}Descriptive Statistics for Categorical Variables}
\centering
\begin{tabular}{llrr}
\toprule
  &    & N & Percent\\
\midrule
Gender & Female & 418 & \num{44.09}\\
 & Male & 524 & \num{55.27}\\
 & Other & 6 & \num{0.63}\\
Highest Education Level & Graduate or professional degree & 145 & \num{15.30}\\
 & Bachelor's degree & 560 & \num{59.07}\\
 & Associate's or Technical degree & 72 & \num{7.59}\\
 & Some college & 100 & \num{10.55}\\
 & High school graduate & 68 & \num{7.17}\\
 & Less than high school & 3 & \num{0.32}\\
Plan to be Vaccinated if not & Probably not & 38 & \num{4.01}\\
 & Definitely yes & 13 & \num{1.37}\\
 & Definitely not & 61 & \num{6.43}\\
 & Might or might not & 22 & \num{2.32}\\
 & Probably yes & 13 & \num{1.37}\\
Found Info Sought Useful & Very useful & 345 & \num{36.39}\\
 & Moderately useful & 112 & \num{11.81}\\
 & Extremely useful & 264 & \num{27.85}\\
 & Slightly useful & 18 & \num{1.90}\\
 & Not at all useful & 2 & \num{0.21}\\
Census Region & Midwest & 171 & \num{18.04}\\
 & Northeast & 170 & \num{17.93}\\
 & South & 365 & \num{38.50}\\
 & West & 223 & \num{23.52}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}
